Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-29 manuscript.Rmd
Add table legends and fix subscripts

Equation 1 identifies the inverse frequency weighting of each overlapping word ti between two tweets d_1 and d_2, relative to the word’s frequency in the corpus D, for all overlapping words t1...k between the two tweets.

@@

Equation 2 then calculates the inverse frequency of each word ti  in tweets d_1 and d_2, relative to the word’s frequency in the corpus D, for all words t1...n that appear in either tweet.

@@

Using the real deciled time series of social cohesion, count of all events, count of
positive events, and count of negative events, we conducted a series of
permutation tests (one for the comparison between social cohesion and each type
of event count) to determine statistical difference from chance for each CRQA
metric. Using the `sample` function in base R [@R-base], $1000$ permuted time
series were created for each of the real time series. CRQA was then run $1000$
times for social cohesion and count of all events, social cohesion and count of
positive events, and social cohesion and count of negative events using the
permuted time series. This resulted in $1000$ results for each of the CRQA
metrics for each combination of time series. Statistical significance from
chance was set at the 95th and 99th percentiles of the metrics from the permuted
CRQ analyses. Given that a permutation test is similar to bootstrapping but does not include replacement, all real recurrent points were included in each CRQA analysis, leaving RR constant across all permutations. Thus, RR is not included in the inferential stests.

@@

# build table
pander(target_results, caption = "\\label{table-1}CRQA results for target-only data.")

@@

# build table
pander(source_target_results, caption = "\\label{table-2}CRQA results for source and target data.")

@@

## Cross-Recurrence Quantification Analysis
### Syria as Target
The significant result of DET and NRLINE for social cohesion with all events
supports our first hypothesis that event activity is coupled with online social
cohesion. The frequency of all events are thus associated with
greater shared trajectories with social cohesion than would be expected by
chance. This could be due to a conflation of the different kinds of events. However, when we specifically target positive events, the coupling with social cohesion is strong, running counter to our second hypothesis. In addition to the significant DET and NRLINE metrics seen in the all-events analysis, maxL and TT are significant for positive events, suggesting a more stable relationship. This may be a reflection of citizens' reaction to events that align with their cause. An act of concession by the government or aid from another country may have led to an increase in morale or feelings of hope, in turn leading to an uproar on Twitter in an attempt to boost morale. By contrast, negative event frequency showed weak coupling, counter to our third hypothesis. Although the significant result for maxL suggests stability, the lack of significant results for other metrics indicate that the maxL metric may point toward a particular period where coupling was strong, although negative events were less coupled for the other points in time. Perhaps during times of intense strife, individuals in Syria focused on real-world action, turning to Twitter to report and rally together. Further text analysis should be conducted to decipher the underlying tone of the tweets.

>>>>

Equation 1 identifies the inverse frequency weighting of each overlapping word $t_i$ between two tweets $d_1$ and $d_2$, relative to the word’s frequency in the corpus D, for all overlapping words $t_{1...k}$ between the two tweets.

@@

Equation 2 then calculates the inverse frequency of each word $t_i$  in tweets $d_1$ and $d_2$, relative to the word’s frequency in the corpus D, for all words $t{1...n}$ that appear in either tweet.

@@

Using the real deciled time series of social cohesion, count of all events, count of
positive events, and count of negative events, we conducted a series of
permutation tests (one for the comparison between social cohesion and each type
of event count) to determine statistical difference from chance for each CRQA
metric. Using the `sample` function in base R [@R-base], $1000$ permuted time
series were created for each of the real time series. CRQA was then run $1000$
times for social cohesion and count of all events, social cohesion and count of
positive events, and social cohesion and count of negative events using the
permuted time series. This resulted in $1000$ results for each of the CRQA
metrics for each combination of time series. Statistical significance from
chance was set at the 95th and 99th percentiles of the metrics from the permuted
CRQ analyses. Given that a permutation test is similar to bootstrapping but does not include replacement, all real recurrent points were included in each CRQA analysis, leaving RR constant across all permutations. Thus, RR is not included in the inferential tests.

@@

# build table
pander(target_results, caption = "\\label{table-1}CRQA results for target-only data.\n. p < .10, * p < .05, ** p < .001")

@@

# build table
pander(source_target_results, caption = "\\label{table-2}CRQA results for source and target data.\n. p < .10, * p < .05, ** p < .001")

@@

## Cross-Recurrence Quantification Analysis
### Syria as Target
The significant result of DET and NRLINE for social cohesion with all events
supports our first hypothesis that event activity is coupled with online social
cohesion. The frequency of all events are thus associated with
greater shared trajectories with social cohesion than would be expected by
chance. This could be due to a conflation of the different kinds of events. However, when we specifically target positive events, the coupling with social cohesion is strong, running counter to our second hypothesis. In addition to the significant DET and NRLINE metrics seen in the all-events analysis, maxL and TT are significant for positive events, suggesting a more stable relationship. This may be a reflection of citizens' reaction to events that align with their cause. An act of concession by the government or aid from another country may have led to an increase in morale or feelings of hope, in turn leading to a groundswell of support on Twitter in an attempt to boost morale. By contrast, negative event frequency showed weak coupling, counter to our third hypothesis. Although the significant result for maxL suggests stability, the lack of significant results for other metrics indicate that the maxL metric may point toward a particular period where coupling was strong, although negative events were less coupled for the other points in time. Perhaps during times of intense strife, individuals in Syria focused on real-world action, turning to Twitter to report and rally together. Further text analysis should be conducted to decipher the underlying tone of the tweets.
